\subsection{The specialisation map}

The main idea of the specialisation method 
is to build a way to transport properties
between the generic fibre and the special fibre.
We consider the following situation.

\begin{situation} \label{sit-5-specialise}
    Let $A$ be a discrete valuation ring,
    with fraction field $\bbK$ and residue field $\bbk$.
    Let $\mathscr{X}$ be an $A$-scheme. Suppose that
    \begin{itemize}
        \item
            The special fibre $X^{\mathrm{s}} = \mathscr{X} \times_A \bbk$ is a $\bbk$-variety.
        \item
            The generic fibre $X = \mathscr{X} \times_A \bbK$ is a $\bbK$-variety.
    \end{itemize}
\end{situation}

After Colliot-Thélène and Pirutka \cite{CTP},
we introduce the specialisation map on the Chow groups.

\begin{proposition} \label{thm-5-spe-map}
    In Situation \textup{\ref{sit-5-specialise}}, 
    there is a \term{specialisation map}
    \[ \sigma \: \CH_0 (X) \to \CH_0 (X^{\mathrm{s}}), \]
    which preserves the degree of $0$-cycles.
\end{proposition}

\begin{proof}
    By \cite[\S1.8 and \S20.1]{fulton}, there is an exact sequence
    \[ \CH_1 (X^{\mathrm{s}}) \overset{i_*}{\longrightarrow} \CH_1 (\mathscr{X})
        \overset{j^*}{\longrightarrow} \CH_0 (X) \to 0, \]
    where $i, j$ are the obvious inclusions.
    (The last term is $\CH_0$ instead of $\CH_1$,
    since $\Spec \bbK$ is a $1$-dimensional point in $\Spec A$.)

    By \cite[\S2.6 and \S20.1]{fulton},
    there is a Gysin map
    \[ i^! \: \CH_1 (\mathscr{X}) \to \CH_0 (X^{\mathrm{s}}), \]
    given by intersection with the divisor $X^{\mathrm{s}}$ of $\mathscr{X}$.
    By \cite[Proposition~2.6~(c)]{fulton},
    we have $i^! \circ i_* = 0$.
    Thus the map $i^!$ factors through the cokernel of $i_*$, giving the desired map.
\end{proof}

\begin{lemma} \label{lem-5-lifting}
    In Situation \textup{\ref{sit-5-specialise}}, suppose that $A$ is henselian,
    and $\mathscr{X}$ is proper and flat over $A$.
    Let $X^{\mathrm{s}}_{\mathrm{sm}} \subset X^{\mathrm{s}}$ be the open set where $X^{\mathrm{s}}$ is smooth.
    Then every $0$-cycle of $X^{\mathrm{s}}$ supported in $X^{\mathrm{s}}_{\mathrm{sm}}$ 
    can be lifted along the specialisation map
    \[ \sigma \: \CH_0 (X) \to \CH_0 (X^{\mathrm{s}}) \]
    to a $0$-cycle supported in $X_{\mathrm{sm}}$.
\end{lemma}

\begin{proof}
    We follow \cite[\S4]{EKW}.
    It is enough to lift the closed points of $X^{\mathrm{s}}_{\mathrm{sm}}$.
    Let $x \in X^{\mathrm{s}}_{\mathrm{sm}}$ be a closed point,
    and let $a_1, \dotsc, a_n \in \mathscr{O}_{X^{\mathrm{s}},x}$ be a regular sequence generating the maximal ideal.
    Choose liftings $\bar{a}_1, \dotsc, \bar{a}_n \in \mathscr{O}_{\mathscr{X},x}$.
    Since $\mathscr{O}_{X^{\mathrm{s}},x} \simeq \mathscr{O}_{\mathscr{X},x} / \pi \mathscr{O}_{\mathscr{X},x}$,
    where $\pi \in A$ is a uniformiser,
    it follows that $\pi, \bar{a}_1, \dotsc, \bar{a}_n$ is a regular sequence in 
    the $(n+1)$-dimensional local ring $\mathscr{O}_{\mathscr{X},x}$.
    Therefore, the ideal $(\bar{a}_1, \dotsc, \bar{a}_n) \subset \mathscr{O}_{\mathscr{X},x}$
    defines a $1$-dimensional subset of $\Spec \mathscr{O}_{\mathscr{X},x}$,
    whose closure in $\mathscr{X}$ is a $1$-dimensional subscheme $Z \subset \mathscr{X}$.
    Then $Z$ is flat of relative dimension $0$ over $A$,
    and hence quasi-finite over $A$. By properness, it is finite over $A$.
    It follows that $Z \simeq \Spec B$ for a finite $A$-algebra $B$.
    Since $A$ is henselian, $B$ is a product of local rings.
    Therefore, the irreducible component of $Z$ containing $x$
    meets $X^{\mathrm{s}}$ at a single point $x$.
    The corresponding $0$-cycle of $X$ has the desired property.
\end{proof}

\begin{lemma} \label{lem-5-henselian}
    In Situation \textup{\ref{sit-5-specialise}}, suppose that
    \begin{itemize}
        \item
            $A$ is henselian, and $\mathscr{X}$ is proper and flat over $A$.
        \item
            The generic fibre $X$ has a desingularisation $p \: \widetilde{X} \to X$,
            such that $\widetilde{X}$ is universally $\CH_0$-trivial.
    \end{itemize}
    Then every $0$-cycle of $X^{\mathrm{s}}$ of degree $0$,
    supported in the open set $X^{\mathrm{s}}_{\mathrm{sm}} \subset X^{\mathrm{s}}$ where $X^{\mathrm{s}}$ is smooth,
    is zero in $\CH_0 (X^{\mathrm{s}})$.
\end{lemma}

\begin{proof}
    Let $U \subset X$ be a dense open set
    such that $p \: p^{-1} (U) \to U$ is an isomorphism.
    Let $x$ be a $0$-cycle of $X^{\mathrm{s}}_{\mathrm{sm}}$ of degree $0$.
    By Lemma~\ref{lem-5-lifting}, $x$ lifts to a $0$-cycle of $X_{\mathrm{sm}}$ of degree $0$.
    By the moving lemma \ref{lem-2-moving},
    it is equivalent to a $0$-cycle supported in $U$,
    which then lifts to a $0$-cycle of $\widetilde{X}$.
    This $0$-cycle is equivalent to $0$ in $\widetilde{X}$ by hypothesis.
    Therefore, applying the map
    \[ \CH_0 (\widetilde{X}) \overset{p_*}{\longrightarrow} \CH_0 (X) 
        \overset{\sigma}{\longrightarrow} \CH_0 (X^{\mathrm{s}}), \]
    we see that $x = 0$ in $\CH_0 (X^{\mathrm{s}})$.
\end{proof}


\subsection{Rationality and specialisation}

The main result is that the rationality 
(or more precisely, universal $\CH_0$-triviality) 
of the generic fibre 
can be specialised to the special fibre,
so that once we show that the special fibre is irrational,
we know that the generic fibre is also irrational.

First, we make clear what we need
to obtain universal triviality for a desingularisation.

\begin{lemma} \label{lem-5-crit-triv}
    Let $f \: \widetilde{X} \to X$ be a desingularisation map between 
    two projective, geometrically integral $\bbk$-varieties. Suppose that 
    \begin{itemize}
        \item
            $\widetilde{X}$ has a $0$-cycle of degree $1$.
        \item
            $f$ is universally $\CH_0$-trivial.
        \item
            There exists an open set $U \subset X$, with $\widetilde{U} = f^{-1} (U)$,
            such that $f \: \widetilde{U} \to U$ is an isomorphism,
            and for any extension $F/\bbk$,
            every $0$-cycle of degree $0$ supported in $U_F$
            is rationally equivalent to zero in $X_F$.
    \end{itemize}
    Then $\widetilde{X}$ is universally $\CH_0$-trivial.
\end{lemma}

\begin{proof}
    Since the conditions of the lemma is preserved by a base change, 
    we only need to prove that $\deg_{\bbk} \: \CH_0 (\widetilde{X}) \to \bbZ$
    is an isomorphism. By the first hypothesis, this map is surjective.
    Thus, it suffices to show that for every $0$-cycle $x$ of $\widetilde{X}$
    of degree $0$, $x$ is rationally equivalent to $0$.
    But by the moving lemma \ref{lem-2-moving},
    it is equivalent to one supported in $\widetilde{U}$,
    which induces a cycle in $U$, which is equivalent to $0$ in $X$ by hypothesis.
    Since $f$ is universally $\CH_0$-trivial,
    $x$ is equivalent to $0$ in $\widetilde{X}$.
\end{proof}

Before the main theorem,
we mention a convenient result in commutative algebra.

\begin{lemma} \label{lem-5-dvr}
    Let $A$ be a discrete valuation ring with residue field $\bbk$,
    and let $F/\bbk$ be an extension.
    Then there exists a complete discrete valuation ring $B$ with residue field $F$,
    together with a local map $A \to B$ inducing the field map $\bbk \to F$.
\end{lemma}

See \cite[Chapter~IX, Appendix, \S2, Corollary, and Exercise~4]{bourbaki-commutative}.

\begin{theorem} [Colliot-Thélène and Pirutka] \label{thm-5-spe-1}
    In Situation \textup{\ref{sit-5-specialise}}, suppose that
    \begin{itemize}
        \item
            $\mathscr{X}$ is faithfully flat and proper over $A$,
            with geometrically integral fibres.
        \item
            The special fibre $X^{\mathrm{s}}$
            has a desingularisation $f \: \widetilde{X}^{\mathrm{s}} \to X^{\mathrm{s}}$,
            such that $f$ is universally $\CH_0$-trivial,
            and $\widetilde{X}^{\mathrm{s}}$ has a $0$-cycle of degree $1$.
        \item
            The generic fibre $X$ 
            has a desingularisation $\widetilde{X} \to X$.
    \end{itemize}
    Then if $\widetilde{X}$ is universally $\CH_0$-trivial, so is $\widetilde{X}^{\mathrm{s}}$.
\end{theorem}

\begin{proof}
    The proof is done by putting the previous lemmas together.

    \begin{itemize}
        \item    
            By Theorem~\ref{thm-2-decomp}, it suffices to show that
            $\widetilde{X}^{\mathrm{s}}_{\bbk (X^{\mathrm{s}})}$ is $\CH_0$-trivial,
            where we notice that $\bbk (\smash{\widetilde{X}^{\mathrm{s}}}) \simeq \bbk (X^{\mathrm{s}})$.
        \item
            By Lemma~\ref{lem-5-crit-triv}, it suffices to show that
            the open set $U = (X^{\mathrm{s}}_{\bbk (X^{\mathrm{s}})})_{\mathrm{sm}} \subset X^{\mathrm{s}}_{\bbk (X^{\mathrm{s}})}$
            satisfies the third assumption of Lemma~\ref{lem-5-crit-triv}.
        \item
            By Lemma~\ref{lem-5-henselian}, it suffices to show that
            $X^{\mathrm{s}}_{\bbk (X^{\mathrm{s}})}$ can act the rôle of $X^{\mathrm{s}}$ in that lemma.
        \item
            By Lemma~\ref{lem-5-dvr}, we take a complete discrete valuation ring $B$,
            with residue field $\bbk (X^{\mathrm{s}})$, and a local map $A \to B$
            inducing the map of fields $\bbk \to \bbk (X^{\mathrm{s}})$.
            Then $B$ is henselian.
            Doing a base change along the map $A \to B$ for everything will complete the proof.
            \qedhere
    \end{itemize}
\end{proof}

There is a stronger variant of this result,
which considers the geometrical generic fibre over $\bbKbar$,
instead of over $\bbK$.
Before introducing the result, we need a lemma.

\begin{lemma} \label{lem-5-fin-ext}
    Let $X$ be a smooth, integral, projective $\bbk$-variety.
    If $X_{\bbkbar}$ is universally $\CH_0$-trivial,
    then $X_F$ is universally $\CH_0$-trivial for some finite extension $F/\bbk$.
\end{lemma}

\begin{proof}
    By Theorem~\ref{thm-2-decomp}, $X_{\bbkbar}$ has a decomposition of the diagonal
    \[ [\Delta_{X_{\bbkbar}}] = D_{\bbkbar} + [X_{\bbkbar}] \times x_0
        \quad \text{in } \CH_n (X_{\bbkbar} \times_{\bbkbar} X_{\bbkbar}). \]
    By Galois descent, there exists a finite extension $F / \bbk$
    over which everything in the equation is defined, 
    and we have 
    \[ \CH_n (X_{\bbkbar} \times_{\bbkbar} X_{\bbkbar}) =
        \colim_{E/F \text{ finite}} \CH_n (X_E \times_E X_E). \]
    Therefore, there exists a finite extension $E$ such that 
    the equation of the decomposition of the diagonal holds over $E$.
\end{proof}

\begin{theorem} [Colliot-Thélène and Pirutka] \label{thm-5-spe-2}
    In Situation \textup{\ref{sit-5-specialise}}, suppose that
    \begin{itemize}
        \item
            The residue field $\bbk$ is algebraically closed.
        \item
            $\mathscr{X}$ is faithfully flat and proper over $A$,
            with geometrically integral fibres.
        \item
            The special fibre $X^{\mathrm{s}}$ 
            has a desingularisation $f \: \widetilde{X}^{\mathrm{s}} \to X^{\mathrm{s}}$,
            such that $f$ is universally $\CH_0$-trivial.
        \item
            The geometrical generic fibre $\Xbar = \mathscr{X} \times_A \bbKbar$
            is a $\bbKbar$-variety,
            with a desingularisation $\widetilde{X} \to \Xbar$.
    \end{itemize}
    Then if $\widetilde{X}$ is universally $\CH_0$-trivial, so is $\widetilde{X}^{\mathrm{s}}$.
\end{theorem}

\begin{proof}
    Our plan is to find a suitable base change in order to apply Theorem~\ref{thm-5-spe-1}.

    First, we replace $A$ by its completion.

    Let $F$ be a finite extension of $\bbK$, on which $\widetilde{X}$ is defined.
    In other words, there exists a smooth variety $Y$ over $F$,
    such that $Y_{\bbKbar} \simeq \widetilde{X}$,
    and there is a desingularisation map $Y \to X_F$, 
    which coincides with the map $\widetilde{X} \to \Xbar$ over $\bbKbar$.

    By Lemma~\ref{lem-5-fin-ext}, we may replace $F$ by a finite extension of it,
    so we may assume that $Y$ is universally $\CH_0$-trivial.

    Let $B$ be the integral closure of $A$ in $F$.
    By \cite[Proposition~I.3]{serre-local},
    $B$ is also a discrete valuation ring.
    Since $\bbk$ is algebraically closed, the residue field of $B$ is also $\bbk$.
    We can thus do a base change along the map $A \to B$, 
    and apply Theorem~\ref{thm-5-spe-1} to complete the proof.
\end{proof}

There is an even stronger variant of this result,
where instead of $\bbKbar$, we consider any field containing $\bbKbar$.

\begin{lemma} \label{lem-5-fin-ext-rational}
    Let $X$ be a projective $\bbk$-variety.
    If $X_F$ is retract rational for some extension $F/\bbk$,
    then the same is true for a certain finite extension $F/\bbk$.
\end{lemma}

\begin{proof}
    In the definition of the retract rationality of $X_F$, 
    everything is defined over a finitely generated extension of $\bbk$.
    Thus we may assume $F/\bbk$ is finitely generated.

    For the same reason, the lemma is true when $F$ is the algebraic closure of~$\bbk$.
    Therefore, we may assume that $\bbk$ is algebraically closed.

    In this case, there exists a $\bbk$-variety $Y$ such that $F$ is isomorphic to $\bbk (Y)$,
    and there exist non-empty open sets $U \subset X \times_{\bbk} Y$ and $V \subset \bbP_Y^n$,
    such that $U$ is a retract of $V$ as a $Y$-scheme.
    There exists a closed point $y \in Y$ such that the fibres $U_y$ and $V_y$ are non-empty.
    This proves the lemma.
\end{proof}

\begin{theorem} [Colliot-Thélène and Pirutka] \label{thm-5-spe-3}
    Assume that the four assumptions of Theorem~\textup{\ref{thm-5-spe-2}} are satisfied.
    Then, if $\widetilde{X}_F$ is retract rational for a field $F$ containing $\bbKbar$,
    then $\widetilde{X}^{\mathrm{s}}$ is universally $\CH_0$-trivial. \qed
\end{theorem}

